\ttitle

### 2015-08-26 Chapters/Introduction.tex
3 days to submission
- Had a long chat with dad
- Had a long chat with Mo - thanks man
- Final review tomorrow
- Aim to submit on Thursday
Introduction - Rajeev comments and a few other minor edits

Haemorrhage is often secondary to non-healing of the pancreatico-jejunal anastomosis leading to leakage of amylase-rich pancreatic juices into the retroperitoneum or secondary to intra-abdominal sepsis or bile leak \parencite{tien_risk_2005, koukoutsis_haemorrhage_2006, choi_delayed_2004, balladur_bleeding_1996}. 
This can then lead to erosion of ligated blood vessels, most commonly the stump of the gastro-duodenal artery. 
Post-pancreatectomy haemorrhage is usually managed with angiographic embolisation of the bleeding vessel and surgical intervention is only rarely required. 
The grading of severity of post-pancreatectomy haemorrhage as described by the International Study Group of Pancreatic Surgery \parencite{wente_postpancreatectomy_2007} is shown in Table \ref{table:isgps_pph} on p\pageref{table:isgps_pph}. .

@@

\subsection{Liver transplantation}
Peak $\dot{V}_{O_2}<60\%$ predicted and $\dot{V}_{O_2}AT<50\%$ predicted have been reported to be associated with increased 100-day mortality in patients undergoing liver transplantation. 
In patients with cirrhosis awaiting hepatic transplantation, reduced aerobic capacity may not only be due to primary cardiorespiratory insufficiency but may also be due to the secondary effects of hepatic dysfunction itself. 
These include cirrhotic cardiomyopathy, hepatopulmonary syndrome and decreased peripheral oxygen utilisation due to cirrhotic myopathy \parencite{epstein_aerobic_2004}. 
This is further supported by the fact that patients who undergo liver transplantation have been shown to have improved aerobic capacity a year after surgery \parencite{iscar_functional_2009}. . 
However, there is very little other evidence of the application of cardiopulmonary exercise testing in patients undergoing major hepato-pancreato-biliary surgery or liver transplantation.

@@

In a study of 207 patients undergoing surgery for Duke's B colorectal cancer, Katoh and co-workers reported that anastomotic leakage and persistently elevated CRP two weeks after surgery were independent risk factors for systemic recurrence, further emphasising the important role of inflammation in cancer recurrence as a consequence of complications \parencite{katoh_anastomotic_2011}. 
Wound infections and intra-abdominal infections have also been associated with poorer survival in colorectal cancer patients \parencite{nespoli_impact_2006}. 
Similar findings have been reported after curative surgery for advanced gastric cancer with patients who develop an anastomotic leak surviving for 30.5 months while patients who did not have a leak survived for a median of 96.2 months (p$<$0.001) \parencite{yoo_negative_2011}. .

@@

Obstructive jaundice is associated with a wide range of deleterious effects on the immune system. 
The absence of bile in the gut increases the proliferation of gram negative bacteria. 
The absence of bile in the gut of bile duct ligated mice was associated with intestinal bacterial overgrowth and bacterial translocation \parencite{deitch_obstructive_1990}

@@

Increased serum bilirubin and bile salts directly affect lymphocyte function as well as the response to pro-inflammatory cytokines \parencite{scott-conner_pathophysiology_1994}
Bile salts in higher than normal concentrations also induce apoptosis in hepatocytes. 
Biliary obstruction is also associated with significant alterations in hepatic macro and micro-circulation. 
This in turn can affect the phagocyte clearing function of the liver. 
Obstructive jaundice is also associated with abnormal cytokine homeostasis predisposing the patient to impaired wound healing, sepsis and increased risk of peri-operative mortality. 
For instance, concentrations of TNF-$\alpha$ and IL-6 are significantly elevated in jaundiced patients while the concentrations of IL-1 and IL-2 are decreased \parencite{padillo_cytokines_2001}.

@@

Mezhir and co-workers also reported a high (23\%) stent related complication rate in their retrospective study of 340 patients where 96\% of 201 patients in the biliary drainage group had plastic stents placed. 
However, they also reported a greater incidence of wound infections (7\% vs 20\%, p=0.01) and intra-abdominal abscesses (3\% vs 12\%, p=0.03) in patients who underwent biliary drainage \parencite{mezhir_matched_2009}

@@

BMI was first devised by Adolphe Quetelet and was formerly known as the Quetelet index \parencite{eknoyan_adolphe_2008}. 
Quetelet was a Belgian sociologist and mathematician who played a major role in the application of statistical methods to the social sciences. 
In his attempts to describe the characteristics of 'normal man', Quetelet found that weight increased nearly as the square of the height except at times of growth spurts in the new born and during puberty \parencite{quetelet_treatise_1842}. . 
The calculation of body mass index is simple and as follows:

>>>>

Haemorrhage is often secondary to non-healing of the pancreatico-jejunal anastomosis leading to leakage of amylase-rich pancreatic juices into the retroperitoneum or secondary to intra-abdominal sepsis or bile leak \parencite{tien_risk_2005, koukoutsis_haemorrhage_2006, choi_delayed_2004, balladur_bleeding_1996}. 
This can then lead to erosion of ligated blood vessels, most commonly the stump of the gastro-duodenal artery. 
Post-pancreatectomy haemorrhage is usually managed with angiographic embolisation of the bleeding vessel and surgical intervention is only rarely required. 
The grading of severity of post-pancreatectomy haemorrhage as described by the International Study Group of Pancreatic Surgery \parencite{wente_postpancreatectomy_2007} is shown in Table \ref{table:isgps_pph} on p\pageref{table:isgps_pph}.

@@

\subsection{Liver transplantation}
Peak $\dot{V}_{O_2}<60\%$ predicted and $\dot{V}_{O_2}AT<50\%$ predicted have been reported to be associated with increased 100-day mortality in patients undergoing liver transplantation. 
In patients with cirrhosis awaiting hepatic transplantation, reduced aerobic capacity may not only be due to primary cardiorespiratory insufficiency but may also be due to the secondary effects of hepatic dysfunction itself. 
These include cirrhotic cardiomyopathy, hepatopulmonary syndrome and decreased peripheral oxygen utilisation due to cirrhotic myopathy \parencite{epstein_aerobic_2004}. 
This is further supported by the fact that patients who undergo liver transplantation have been shown to have improved aerobic capacity a year after surgery \parencite{iscar_functional_2009}. 
However, there is very little other evidence of the application of cardiopulmonary exercise testing in patients undergoing major hepato-pancreato-biliary surgery or liver transplantation.

@@

In a study of 207 patients undergoing surgery for Duke's B colorectal cancer, Katoh and co-workers reported that anastomotic leakage and persistently elevated CRP two weeks after surgery were independent risk factors for systemic recurrence, further emphasising the important role of inflammation in cancer recurrence as a consequence of complications \parencite{katoh_anastomotic_2011}. 
Wound infections and intra-abdominal infections have also been associated with poorer survival in colorectal cancer patients \parencite{nespoli_impact_2006}. 
Similar findings have been reported after curative surgery for advanced gastric cancer with patients who develop an anastomotic leak surviving for 30.5 months while patients who did not have a leak survived for a median of 96.2 months (p$<$0.001) \parencite{yoo_negative_2011}.

@@

Obstructive jaundice is associated with a wide range of deleterious effects on the immune system. 
The absence of bile in the gut increases the proliferation of gram negative bacteria. 
The absence of bile in the gut of bile duct ligated mice was associated with intestinal bacterial overgrowth and bacterial translocation \parencite{deitch_obstructive_1990}.

@@

Increased serum bilirubin and bile salts directly affect lymphocyte function as well as the response to pro-inflammatory cytokines \parencite{scott-conner_pathophysiology_1994}.
Bile salts in higher than normal concentrations also induce apoptosis in hepatocytes. 
Biliary obstruction is also associated with significant alterations in hepatic macro and micro-circulation. 
This in turn can affect the phagocyte clearing function of the liver. 
Obstructive jaundice is also associated with abnormal cytokine homeostasis predisposing the patient to impaired wound healing, sepsis and increased risk of peri-operative mortality. 
For instance, concentrations of TNF-$\alpha$ and IL-6 are significantly elevated in jaundiced patients while the concentrations of IL-1 and IL-2 are decreased \parencite{padillo_cytokines_2001}.

@@

Mezhir and co-workers also reported a high (23\%) stent related complication rate in their retrospective study of 340 patients where 96\% of 201 patients in the biliary drainage group had plastic stents placed. 
However, they also reported a greater incidence of wound infections (7\% vs 20\%, p=0.01) and intra-abdominal abscesses (3\% vs 12\%, p=0.03) in patients who underwent biliary drainage \parencite{mezhir_matched_2009}.

@@

BMI was first devised by Adolphe Quetelet and was formerly known as the Quetelet index \parencite{eknoyan_adolphe_2008}. 
Quetelet was a Belgian sociologist and mathematician who played a major role in the application of statistical methods to the social sciences. 
In his attempts to describe the characteristics of 'normal man', Quetelet found that weight increased nearly as the square of the height except at times of growth spurts in the new born and during puberty \parencite{quetelet_treatise_1842}. 
The calculation of body mass index is simple and as follows:
